00-Data-Preprocessing

### 2021-05-20 R0-Density-Reanalysis/R0-Density-Reanalysis.tex
First draft of background, started working on tobit models; recreated data package to include a common key for the state boundaries

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}

@@

\hypertarget{replicating-swn}{%
\subsection{Replicating SWN}\label{replicating-swn}}

@@

\begin{figure}
\centering
\includegraphics{R0-Density-Reanalysis_files/figure-latex/R0-map-1.pdf}
\caption{\label{fig:R0-map}Basic reproductive rate in US counties
(Alaska, Hawaii, Puerto Rico, and territories not shown).}
\end{figure}

@@

Table \ref{tab:swn-results} replicates Table 1 of SWN (p.~6).

@@

\hypertarget{some-relevant-questions}{%
\section{Some relevant questions}\label{some-relevant-questions}}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{table1model1 }\OtherTok{\textless{}{-}} \FunctionTok{censReg}\NormalTok{(R }\SpecialCharTok{\textasciitilde{}}\NormalTok{ density\_log, }
                        \AttributeTok{left =} \DecValTok{0}\NormalTok{,}
                    \AttributeTok{data =}\NormalTok{ county\_geo\_clean)}
\FunctionTok{summary}\NormalTok{(table1model1)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## censReg(formula = R ~ density_log, left = 0, data = county_geo_clean)
## 
## Observations:
##          Total  Left-censored     Uncensored Right-censored 
##           3218           2067           1151              0 
## 
## Coefficients:
##             Estimate Std. error t value Pr(> t)    
## (Intercept)  2.33967    0.09232   25.34  <2e-16 ***
## density_log  0.74323    0.02672   27.82  <2e-16 ***
## logSigma     0.56894    0.02396   23.74  <2e-16 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Newton-Raphson maximisation, 7 iterations
## Return code 8: successive function values within relative tolerance limit (reltol)
## Log-likelihood: -3246.5 on 3 Df
\end{verbatim}

Linear mixed models of R0 and density + \% private transportation

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{table1model2 }\OtherTok{\textless{}{-}} \FunctionTok{censReg}\NormalTok{(R }\SpecialCharTok{\textasciitilde{}}\NormalTok{ density\_log }\SpecialCharTok{+}\NormalTok{ private, }
                    \AttributeTok{data =}\NormalTok{ county\_geo\_clean)}
\FunctionTok{summary}\NormalTok{(table1model2)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## censReg(formula = R ~ density_log + private, data = county_geo_clean)
## 
## Observations:
##          Total  Left-censored     Uncensored Right-censored 
##           3218           2067           1151              0 
## 
## Coefficients:
##             Estimate Std. error t value Pr(> t)    
## (Intercept) 0.825319   0.583014   1.416 0.15689    
## density_log 0.754516   0.027546  27.391 < 2e-16 ***
## private     0.017186   0.006548   2.624 0.00868 ** 
## logSigma    0.570248   0.023977  23.783 < 2e-16 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Newton-Raphson maximisation, 7 iterations
## Return code 8: successive function values within relative tolerance limit (reltol)
## Log-likelihood: -3242.96 on 4 Df
\end{verbatim}

Linear mixed models of R0 and density + \% private transportation +
median income

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{table1model3 }\OtherTok{\textless{}{-}} \FunctionTok{censReg}\NormalTok{(R }\SpecialCharTok{\textasciitilde{}}\NormalTok{ density\_log }\SpecialCharTok{+}\NormalTok{ private }\SpecialCharTok{+}\NormalTok{ hincome, }
                    \AttributeTok{data =}\NormalTok{ county\_geo\_clean)}
\FunctionTok{summary}\NormalTok{(table1model3)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## censReg(formula = R ~ density_log + private + hincome, data = county_geo_clean)
## 
## Observations:
##          Total  Left-censored     Uncensored Right-censored 
##           3218           2067           1151              0 
## 
## Coefficients:
##              Estimate Std. error t value  Pr(> t)    
## (Intercept) -3.201908   0.680988  -4.702 2.58e-06 ***
## density_log  0.662526   0.026876  24.651  < 2e-16 ***
## private      0.040886   0.006844   5.974 2.32e-09 ***
## hincome      0.297763   0.025726  11.574  < 2e-16 ***
## logSigma     0.531694   0.023920  22.228  < 2e-16 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Newton-Raphson maximisation, 7 iterations
## Return code 8: successive function values within relative tolerance limit (reltol)
## Log-likelihood: -3174.96 on 5 Df
\end{verbatim}

Tobit models of R0 and density + \% private transportation + median
income + interaction of density and \% private transportation

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{table1model4 }\OtherTok{\textless{}{-}} \FunctionTok{censReg}\NormalTok{(R }\SpecialCharTok{\textasciitilde{}}\NormalTok{ density\_log}\SpecialCharTok{*}\NormalTok{private }\SpecialCharTok{+}\NormalTok{ hincome, }
                    \AttributeTok{data =}\NormalTok{ county\_geo\_clean)}
\FunctionTok{summary}\NormalTok{(table1model4)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## censReg(formula = R ~ density_log * private + hincome, data = county_geo_clean)
## 
## Observations:
##          Total  Left-censored     Uncensored Right-censored 
##           3218           2067           1151              0 
## 
## Coefficients:
##                      Estimate Std. error t value  Pr(> t)    
## (Intercept)         -3.687016   0.733410  -5.027 4.98e-07 ***
## density_log          0.311841   0.174521   1.787   0.0740 .  
## private              0.047454   0.007712   6.154 7.58e-10 ***
## hincome              0.291536   0.025807  11.297  < 2e-16 ***
## density_log:private  0.004097   0.002028   2.020   0.0434 *  
## logSigma             0.530095   0.023924  22.158  < 2e-16 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Newton-Raphson maximisation, 7 iterations
## Return code 8: successive function values within relative tolerance limit (reltol)
## Log-likelihood: -3173.008 on 6 Df
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Fit SAR Tobit}
\NormalTok{fit\_sartobit }\OtherTok{\textless{}{-}} \FunctionTok{sartobit}\NormalTok{(R }\SpecialCharTok{\textasciitilde{}}\NormalTok{ density\_log }\SpecialCharTok{+}\NormalTok{ private }\SpecialCharTok{+}\NormalTok{ hincome\_log,}
\NormalTok{                         B,}
                         \AttributeTok{ndraw =} \DecValTok{1000}\NormalTok{,}
                         \AttributeTok{burn.in =} \DecValTok{200}\NormalTok{, }
                         \AttributeTok{showProgress =} \ConstantTok{TRUE}\NormalTok{,}
                         \AttributeTok{data =}\NormalTok{ county\_geo\_clean,}
                         \AttributeTok{computeMarginalEffects =} \ConstantTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning in model.matrix.default(mt, mf, contrasts): non-list contrasts argument
## ignored
\end{verbatim}

\begin{verbatim}
## Warning: Function SE_classic_setup moved to the spatialreg package
\end{verbatim}

\begin{verbatim}
## Registered S3 methods overwritten by 'spatialreg':
##   method                   from 
##   residuals.stsls          spdep
##   deviance.stsls           spdep
##   coef.stsls               spdep
##   print.stsls              spdep
##   summary.stsls            spdep
##   print.summary.stsls      spdep
##   residuals.gmsar          spdep
##   deviance.gmsar           spdep
##   coef.gmsar               spdep
##   fitted.gmsar             spdep
##   print.gmsar              spdep
##   summary.gmsar            spdep
##   print.summary.gmsar      spdep
##   print.lagmess            spdep
##   summary.lagmess          spdep
##   print.summary.lagmess    spdep
##   residuals.lagmess        spdep
##   deviance.lagmess         spdep
##   coef.lagmess             spdep
##   fitted.lagmess           spdep
##   logLik.lagmess           spdep
##   fitted.SFResult          spdep
##   print.SFResult           spdep
##   fitted.ME_res            spdep
##   print.ME_res             spdep
##   print.lagImpact          spdep
##   plot.lagImpact           spdep
##   summary.lagImpact        spdep
##   HPDinterval.lagImpact    spdep
##   print.summary.lagImpact  spdep
##   print.sarlm              spdep
##   summary.sarlm            spdep
##   residuals.sarlm          spdep
##   deviance.sarlm           spdep
##   coef.sarlm               spdep
##   vcov.sarlm               spdep
##   fitted.sarlm             spdep
##   logLik.sarlm             spdep
##   anova.sarlm              spdep
##   predict.sarlm            spdep
##   print.summary.sarlm      spdep
##   print.sarlm.pred         spdep
##   as.data.frame.sarlm.pred spdep
##   residuals.spautolm       spdep
##   deviance.spautolm        spdep
##   coef.spautolm            spdep
##   fitted.spautolm          spdep
##   print.spautolm           spdep
##   summary.spautolm         spdep
##   logLik.spautolm          spdep
##   print.summary.spautolm   spdep
##   print.WXImpact           spdep
##   summary.WXImpact         spdep
##   print.summary.WXImpact   spdep
##   predict.SLX              spdep
\end{verbatim}

\begin{verbatim}
##   |                                                                              |                                                                      |   0%  |                                                                              |                                                                      |   1%  |                                                                              |=                                                                     |   1%  |                                                                              |=                                                                     |   2%  |                                                                              |==                                                                    |   2%  |                                                                              |==                                                                    |   3%  |                                                                              |==                                                                    |   4%  |                                                                              |===                                                                   |   4%  |                                                                              |===                                                                   |   5%  |                                                                              |====                                                                  |   5%  |                                                                              |====                                                                  |   6%  |                                                                              |=====                                                                 |   6%  |                                                                              |=====                                                                 |   7%  |                                                                              |=====                                                                 |   8%  |                                                                              |======                                                                |   8%  |                                                                              |======                                                                |   9%  |                                                                              |=======                                                               |   9%  |                                                                              |=======                                                               |  10%  |                                                                              |=======                                                               |  11%  |                                                                              |========                                                              |  11%  |                                                                              |========                                                              |  12%  |                                                                              |=========                                                             |  12%  |                                                                              |=========                                                             |  13%  |                                                                              |=========                                                             |  14%  |                                                                              |==========                                                            |  14%  |                                                                              |==========                                                            |  15%  |                                                                              |===========                                                           |  15%  |                                                                              |===========                                                           |  16%  |                                                                              |============                                                          |  16%  |                                                                              |============                                                          |  17%  |                                                                              |============                                                          |  18%  |                                                                              |=============                                                         |  18%  |                                                                              |=============                                                         |  19%  |                                                                              |==============                                                        |  19%  |                                                                              |==============                                                        |  20%  |                                                                              |==============                                                        |  21%  |                                                                              |===============                                                       |  21%  |                                                                              |===============                                                       |  22%  |                                                                              |================                                                      |  22%  |                                                                              |================                                                      |  23%  |                                                                              |================                                                      |  24%  |                                                                              |=================                                                     |  24%  |                                                                              |=================                                                     |  25%  |                                                                              |==================                                                    |  25%  |                                                                              |==================                                                    |  26%  |                                                                              |===================                                                   |  26%  |                                                                              |===================                                                   |  27%  |                                                                              |===================                                                   |  28%  |                                                                              |====================                                                  |  28%  |                                                                              |====================                                                  |  29%  |                                                                              |=====================                                                 |  29%  |                                                                              |=====================                                                 |  30%  |                                                                              |=====================                                                 |  31%  |                                                                              |======================                                                |  31%  |                                                                              |======================                                                |  32%  |                                                                              |=======================                                               |  32%  |                                                                              |=======================                                               |  33%  |                                                                              |=======================                                               |  34%  |                                                                              |========================                                              |  34%  |                                                                              |========================                                              |  35%  |                                                                              |=========================                                             |  35%  |                                                                              |=========================                                             |  36%  |                                                                              |==========================                                            |  36%  |                                                                              |==========================                                            |  37%  |                                                                              |==========================                                            |  38%  |                                                                              |===========================                                           |  38%  |                                                                              |===========================                                           |  39%  |                                                                              |============================                                          |  39%  |                                                                              |============================                                          |  40%  |                                                                              |============================                                          |  41%  |                                                                              |=============================                                         |  41%  |                                                                              |=============================                                         |  42%  |                                                                              |==============================                                        |  42%  |                                                                              |==============================                                        |  43%  |                                                                              |==============================                                        |  44%  |                                                                              |===============================                                       |  44%  |                                                                              |===============================                                       |  45%  |                                                                              |================================                                      |  45%  |                                                                              |================================                                      |  46%  |                                                                              |=================================                                     |  46%  |                                                                              |=================================                                     |  47%  |                                                                              |=================================                                     |  48%  |                                                                              |==================================                                    |  48%  |                                                                              |==================================                                    |  49%  |                                                                              |===================================                                   |  49%  |                                                                              |===================================                                   |  50%  |                                                                              |===================================                                   |  51%  |                                                                              |====================================                                  |  51%  |                                                                              |====================================                                  |  52%  |                                                                              |=====================================                                 |  52%  |                                                                              |=====================================                                 |  53%  |                                                                              |=====================================                                 |  54%  |                                                                              |======================================                                |  54%  |                                                                              |======================================                                |  55%  |                                                                              |=======================================                               |  55%  |                                                                              |=======================================                               |  56%  |                                                                              |========================================                              |  56%  |                                                                              |========================================                              |  57%  |                                                                              |========================================                              |  58%  |                                                                              |=========================================                             |  58%  |                                                                              |=========================================                             |  59%  |                                                                              |==========================================                            |  59%  |                                                                              |==========================================                            |  60%  |                                                                              |==========================================                            |  61%  |                                                                              |===========================================                           |  61%  |                                                                              |===========================================                           |  62%  |                                                                              |============================================                          |  62%  |                                                                              |============================================                          |  63%  |                                                                              |============================================                          |  64%  |                                                                              |=============================================                         |  64%  |                                                                              |=============================================                         |  65%  |                                                                              |==============================================                        |  65%  |                                                                              |==============================================                        |  66%  |                                                                              |===============================================                       |  66%  |                                                                              |===============================================                       |  67%  |                                                                              |===============================================                       |  68%  |                                                                              |================================================                      |  68%  |                                                                              |================================================                      |  69%  |                                                                              |=================================================                     |  69%  |                                                                              |=================================================                     |  70%  |                                                                              |=================================================                     |  71%  |                                                                              |==================================================                    |  71%  |                                                                              |==================================================                    |  72%  |                                                                              |===================================================                   |  72%  |                                                                              |===================================================                   |  73%  |                                                                              |===================================================                   |  74%  |                                                                              |====================================================                  |  74%  |                                                                              |====================================================                  |  75%  |                                                                              |=====================================================                 |  75%  |                                                                              |=====================================================                 |  76%  |                                                                              |======================================================                |  76%  |                                                                              |======================================================                |  77%  |                                                                              |======================================================                |  78%  |                                                                              |=======================================================               |  78%  |                                                                              |=======================================================               |  79%  |                                                                              |========================================================              |  79%  |                                                                              |========================================================              |  80%  |                                                                              |========================================================              |  81%  |                                                                              |=========================================================             |  81%  |                                                                              |=========================================================             |  82%  |                                                                              |==========================================================            |  82%  |                                                                              |==========================================================            |  83%  |                                                                              |==========================================================            |  84%  |                                                                              |===========================================================           |  84%  |                                                                              |===========================================================           |  85%  |                                                                              |============================================================          |  85%  |                                                                              |============================================================          |  86%  |                                                                              |=============================================================         |  86%  |                                                                              |=============================================================         |  87%  |                                                                              |=============================================================         |  88%  |                                                                              |==============================================================        |  88%  |                                                                              |==============================================================        |  89%  |                                                                              |===============================================================       |  89%  |                                                                              |===============================================================       |  90%  |                                                                              |===============================================================       |  91%  |                                                                              |================================================================      |  91%  |                                                                              |================================================================      |  92%  |                                                                              |=================================================================     |  92%  |                                                                              |=================================================================     |  93%  |                                                                              |=================================================================     |  94%  |                                                                              |==================================================================    |  94%  |                                                                              |==================================================================    |  95%  |                                                                              |===================================================================   |  95%  |                                                                              |===================================================================   |  96%  |                                                                              |====================================================================  |  96%  |                                                                              |====================================================================  |  97%  |                                                                              |====================================================================  |  98%  |                                                                              |===================================================================== |  98%  |                                                                              |===================================================================== |  99%  |                                                                              |======================================================================|  99%  |                                                                              |======================================================================| 100%
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{summary}\NormalTok{(fit\_sartobit)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## ----MCMC spatial autoregressive Tobit model ----
## Execution time  = 41.022 secs
## 
## N draws         =   1000, N omit (burn-in)=    200
## N observations  =   3218, K covariates    =      4
## # censored values =   2067, # observed values =   1151
## Min rho         = -1.000, Max rho         =  1.000
## --------------------------------------------------
## 
##              Estimate  Std. Dev   p-level t-value Pr(>|z|)    
## (Intercept) -4.399260  0.737342  0.000000  -5.966 2.69e-09 ***
## density_log  0.562608  0.026714  0.000000  21.061  < 2e-16 ***
## private      0.039826  0.006874  0.000000   5.794 7.54e-09 ***
## hincome_log  1.572387  0.138627  0.000000  11.343  < 2e-16 ***
## sige         2.992428  0.173624  0.000000  17.235  < 2e-16 ***
## rho          0.056389  0.004937  0.000000  11.421  < 2e-16 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{impacts}\NormalTok{(fit\_sartobit)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## --------Marginal Effects--------
## 
## (a) Direct effects
##             lower_005 posterior_mean upper_095
## density_log   0.21275        0.23102     0.248
## private       0.01180        0.01635     0.021
## hincome_log   0.55351        0.64566     0.744
## 
## (b) Indirect effects
##             lower_005 posterior_mean upper_095
## density_log  -0.29273       -0.27252    -0.251
## private      -0.02504       -0.01929    -0.014
## hincome_log  -0.88010       -0.76178    -0.651
## 
## (c) Total effects
##             lower_005 posterior_mean upper_095
## density_log -0.044493      -0.041495    -0.038
## private     -0.003850      -0.002942    -0.002
## hincome_log -0.136033      -0.116125    -0.097
\end{verbatim}

>>>>

@@

\hypertarget{reproducing-swn}{%
\section{Reproducing SWN}\label{reproducing-swn}}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{R0-Density-Reanalysis_files/figure-latex/R0-map-1} \caption{\label{fig:R0-map}Basic reproductive rate in US counties (Alaska, Hawaii, Puerto Rico, and territories not shown).}\label{fig:R0-map}
\end{figure}

@@

Table \ref{tab:swn-results} replicates the first three models of SWN
(the fourth model did not have any significant variables; see Table 1 in
SNW). It is possible to verify that the results match with the minor
(and irrelevant) exception of the magnitude of the coefficient for
travel by private transportation, which is due to a difference in the
input (here the variable is one percent units, whereas in SWN it was ten
percent units). The intercept in these models is a random variable, and
the standard deviation is reported in the fourth row of Table
\ref{tab:swn-results}. It is useful to map the random intercepts: as
seen in Figure \ref{fig:random-terms-map}, other things being equal,
counties in Texas tended to have somewhat lower values of \(R_0\) (i.e.,
a negative random intercept), whereas counties in South Dakota tended to
have higher values of \(R_0\). The key of the analysis, that population
density has a positive association with the basic reproductive number,
is verified. But is it really?

@@

\begin{figure}
\includegraphics[width=1\linewidth]{R0-Density-Reanalysis_files/figure-latex/random-terms-map-1} \caption{\label{fig:random-terms-map}Random intercepts of Model 3 (Alaska, Hawaii, Puerto Rico, and territories not shown).}\label{fig:random-terms-map}
\end{figure}

\hypertarget{expanding-on-swn}{%
\section{Expanding on SWN}\label{expanding-on-swn}}

Thanks to the availability of code and data, it was possible to verify
the results reported by SWN. As noted earlier, though, an experienced
spatial modeller would have asked themselves about the implications of
the spatial sampling procedure used by SWN. The decision to use a sample
of counties with reliable basic reproductive numbers, although seemingly
sensible, results in a non-random sampling scheme. Turning our attention
back to Figure \ref{fig:R0-map}, we see that many counties without
reliable values of \(R_0\) are in more rural, less dense parts of the
United States. The fact that \(R_0\) could not be accurately computed in
those counties does not mean that there was no transmission of the
virus: it simply means that we do not know with precision whether that
was the case. The low number of cases may be related to low population
and/or low population density. This is intriguing, to say the least: by
excluding cases in a non-random way such as this, we are in effect
\emph{truncating} the sample.

The issue with sample truncation is that parameter estimates can become
unreliable.

@@

\caption{\label{tab:unnamed-chunk-3}\label{tab:tobit-results}Marginal effects of sample selection models}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllllrl}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Tobit Model 1} & \multicolumn{2}{c}{Tobit Model 2} & \multicolumn{2}{c}{Tobit Model 3} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
Variable & m.e. & 95\% CI & m.e. & 95\% CI & m.e. & 95\% CI\\
\midrule
Log of population density & 0.264 & [0.246, 0.281] & 0.264 & [0.247, 0.281] & 0.233 & [0.216, 0.25]\\
Percent of private transportation &  &  & 0.006 & [0.002, 0.01] & 0.014 & [0.01, 0.019]\\
Median household income (\$10,000) &  &  &  &  & 0.105 & [0.087, 0.122]\\
\bottomrule
\end{tabular}}
\end{table}

@@

### 2021-05-20 r0density/raw-data-processing/00-Data-Preprocessing.Rmd
First draft of background, started working on tobit models; recreated data package to include a common key for the state boundaries

Prepare state boundaries for saving
```{r}
state_geo <- state_geo %>%
  select(-CENSUSAREA, -starts_with("geometry"), geometry)
```

>>>>

Prepare state boundaries for saving:
```{r}
# Get state number code and two letter code from county table:
state_key <- county_geo %>% 
  st_drop_geometry() %>%
  drop_na(state) %>% 
  distinct(STATE, 
           .keep_all = TRUE) %>% 
  select(STATE, state)

# Join state two letter code to table:
state_geo <- state_geo %>%
  left_join(state_key,
            by = "STATE")

state_geo <- state_geo %>%
  select(-CENSUSAREA, -starts_with("geometry"), geometry)
```
